Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Spell out data acquisition

Wake velocity was measured using a Nortek Vectrino+ acoustic Doppler velocimeter
(ADV) (Nortek AS, Rud, Norway)}, which has an approximately 6~mm diameter sampling volume and sampled at
200 Hz. The probe was mounted on an automated positioning system, also
controlled by the tow tank's main motion controller. The ADV and \hl {DAQ (please define)} systems'
sampling times were synchronized by triggering the start of data acquisition via
a pulse sent from the motion controller. Additional details of the turbine and
experimental setup are described in \cite{Bachant2015-JoT}.

>>>>

Wake velocity was measured using a Nortek Vectrino+ acoustic Doppler velocimeter
(ADV) (Nortek AS, Rud, Norway), which has an approximately 6~mm diameter
sampling volume and sampled at 200 Hz. The probe was mounted on an automated
positioning system, also controlled by the tow tank's main motion controller.
The ADV and data acquisition systems' sampling times were synchronized by
triggering the start of data acquisition via a pulse sent from the motion
controller. Additional details of the turbine and experimental setup are
described in \cite{Bachant2015-JoT}.
